### 2024-04-17 docs/SOSP 2024/results.tex
Edit results

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_kernel_time.png}
  \caption{\Treebeard{} vs RAPIDs and Tahoe Kernel Time Speedup on NVIDIA RTX 4060}
  \label{Fig:TBvsRAPIDsTahoe_4060_Speedup}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_total_time.png}
  \caption{\Treebeard{} vs RAPIDs Total Time Speedup on NVIDIA RTX 4060.}
  \label{Fig:TBvsRAPIDs_4060_TotalTimeSpeedup}
\end{figure}

@@

\subsection{Autotuning Heuristic}
\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/AutotuningSpeedupvs4060Sched_T400.png}
  \caption{Autotuning heuristics speedup vs best 4060 schedule on T400.}
  \label{Fig:AutotuningSpeedupvs4060Sched_T400}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/HeuristicVsFullExplore_Speedup.png}
  \caption{Autotuning heuristic compile time speedup vs full schedule exploration.}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
  \caption{\Treebeard{} vs RAPIDs and Tahoe kernel time and total time speedup on NVIDIA RTX 4060}
  \label{Fig:TBvsRAPIDsTahoe_4060_Speedup}
\end{figure}

% \begin{figure}[htb]
%   \centering
%   \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_total_time.png}
%   \caption{\Treebeard{} vs RAPIDs Total Time Speedup on NVIDIA RTX 4060.}
%   \label{Fig:TBvsRAPIDs_4060_TotalTimeSpeedup}
% \end{figure}

@@

\subsection{Autotuning Heuristic}
\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_best_vs_at.png}
  \caption{Autotuning heuristics speedup vs best 4060 schedule on NVIDIA RTX 4060}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/AutotuningSpeedupvs4060Sched_T400.png}
  \caption{Autotuning heuristics speedup vs best 4060 schedule on T400.}
  \label{Fig:AutotuningSpeedupvs4060Sched_T400}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\linewidth]{figures/geomean_speedup_4060_full_exp_vs_at.png}
  \caption{Autotuning heuristic compile time speedup vs full schedule exploration.}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

\begin{itemize}
  \item We compare the schedule found by the schedule exploration heuristic on the RTX 4060 with the best schedule found by
  extensive exploration. Figure \ref{Fig:HeuristicVsFullExplore_Speedup} shows that the heuristic is able to find schedules that are
  very close to the best schedule found by exhaustive exploration.
  \item The speedup of the heuristic schedule vs the best 4060 schedule is shown in Figure \ref{Fig:AutotuningSpeedupvs4060Sched}.
  Geomean speedup range from 1.1$\times$ to 1.2$\times$.
  \item 
\end{itemize}
